The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2020-12-23 example.tex
Set size of the tt example code blocks to small to try and fit a bit better in a column
Made reference to footerscroll.pdf file fixed width font

\begin{lstlisting}
\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{DndComment}{Note On Changing Schemes}
If a major color scheme change is attempted, it is
likely that the background ``paper'' (which can be overridden with
|\SetPaperImage|) and footerscroll.pdf will need
to be modified as well in order to fit the other color modifications.
\end{DndComment}

>>>>

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

@@

\begin{DndComment}{Note On Changing Schemes}
If a major color scheme change is attempted, it is
likely that the background ``paper'' (which can be overridden with
|\SetPaperImage|) and |footerscroll.pdf| will need
to be modified as well in order to fit the other color modifications.
\end{DndComment}
